Manuscript_Github_Pchabaudi_pir

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Adding commands to save the figures

#Want the defaults for arrange, mutate and summarise to be from dplyr
arrange <- dplyr::arrange
mutate <- dplyr::mutate
summarise <- dplyr::summarise
select <- dplyr::select
```

```{r tpm, results = 'hide', message = FALSE}
# # Calculating the transcript-per-million 
# 
# We need to write a function to calculate the TPM from the count data we have generated. This function uses the 'chabaudi_transcript_lengths' object created in the chunk above and should generate errors if it detects discrepencies between the Geneids so that the wrong transcript length is not used.

tpm = function(count_data, lengths = chabaudi_transcript_lengths) {

  #Print an error if the id columns do not match
  # first if statement to test that both have a GeneID column
  if(any(grepl(colnames(lengths), 
               pattern = 'id', 
               ignore.case = T)) == T & any(grepl(colnames(count_data), 
                                                  pattern = 'Geneid', 
                                                  #This needs to be Geneid when some of the samples have 'id' in them
                                                  ignore.case = T)) == T){
    if(all(count_data[grep(colnames(count_data), 
                           pattern = 'Geneid', ignore.case = T)] == lengths[grep(colnames(lengths), 
                                                                             pattern = 'id', ignore.case = T)])) {
      print('Count data and length gene ids both match')
    } else {
      stop('Error: Count data and length gene ids DO NOT MATCH, please make sure they are ordered identically.')
    }
  } else {
    stop('Error: Count data and/or length table supplied do not have an id column.')
  }

  #Remove the id column from supplied count_data
  if(any(grepl(colnames(count_data), pattern = 'Geneid',ignore.case = T)) == T){
    counts_tpm = count_data[,-grep(colnames(count_data), pattern = 'Geneid', ignore.case = T)]
  } else{
    counts_tpm <- count_data}

  #Remove the id column from supplied lengths
  if(any(grepl(colnames(lengths), pattern = 'id', ignore.case = T)) == T){
    lengths.table = lengths[,-grep(colnames(lengths), pattern = 'id', ignore.case = T)]
  }else{
    lengths.table <- lengths}
  lengths.table = matrix(lengths.table)
  #This may make lengths.table a vector which can bring up some dimension problems in the following for loop

  #Now for the actual calculation
  rpm <- counts_tpm
  for (i in 1:dim(counts_tpm)[2]) {
    for (j in 1:dim(counts_tpm)[1]) {
      rpm[j,i] <- (counts_tpm[j,i]/(lengths.table[j]/1000))
    }
    scale.factor <- sum(rpm[,i])/(1E6)
    counts_tpm[,i] <- apply(rpm[,i,drop=F],1,function(x){x/scale.factor})
  }
  if(any(grepl(colnames(count_data), pattern = 'Geneid', ignore.case = T)) == T){
    counts_tpm = bind_cols(count_data[,grep(colnames(count_data), pattern = 'Geneid', ignore.case = T), drop = FALSE], 
                           counts_tpm)
  } 
  return(counts_tpm)
}
```

@@

@@

@@

# Phaseograms of all the genes in both transmission methods - supplementary figure 5.

@@

## Phaseograms of the entire genome.

```{r phaseograms_whole_genome}

@@

## Phaseograms of the _cir_ genes with clade annotations. - Supplementary figure 6

@@

@@

## Figure 4 and supplementary figure 7/8

@@

@@

>>>>

#Want the defaults for arrange, mutate and summarise to be from dplyr
arrange <- dplyr::arrange
mutate <- dplyr::mutate
summarise <- dplyr::summarise
select <- dplyr::select

#Global save var - set to TRUE if you want to save figures.
global_save_var <- TRUE
```

@@

         if(global_save_var){        
           pdf('Manuscript_figure3c_heatmap.pdf'
               , width = 10
               , height = 4
           )
           draw(ht_list, 
                row_title_side = 'left',
                column_title_side = 'bottom',
                heatmap_legend_side = 'right',
                annotation_legend_side = 'right',
                annotation_legend_list = list(clade_lgd),
                ht_gap = unit(.35,'cm'),
                merge_legend = TRUE)
           dev.off()
         }

@@

if(global_save_var){
  ggsave2(filename = 'Manuscript_SuppFigure3_chabaudi24h_pca_nopseudo.png',
          plot = plot,
          dpi = 300,
          width = 15,
          height = 10,
          units = 'cm')
}

@@

# Phaseograms of all the genes.

@@

## Supplementary figure 5 - Phaseograms of the entire genome.

```{r phaseograms_whole_genome}
if(global_save_var){
  png(filename = 'Manuscript_SuppFig5_phaseogram_allgenes.png',
      units = 'cm',
      height = 20,
      width = 22,
      res = 330)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

@@

##  Supplementary figure 6 - Phaseograms of the _cir_ genes with clade annotations

@@

if(global_save_var){
  png(filename = 'Manuscript_SuppFig6_phaseogram_cirgenes.png',
      units = 'cm',
      height = 20,
      width = 22,
      res = 200)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      filter_genes_vector = cir_id,
                      annotation_clade = 'SorL',
                      annotation_col = SorL_col,
                      threshold_tpm = 1,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

@@

## Figure 4 and supplementary figure 7

@@

           if(global_save_var){
             ggsave2(
               paste0('Pchabaudi_side-by-side_barchart_facetbySubfam_',
                      time_vec,
                      '.png'),
               plot = g,
               dpi = 300,
               width = 28,
               height = 8,
               units = 'cm'
             )
           }

@@

    if(global_save_var){
      ggsave2(
        paste0('Pchabaudi_sibe-by-side_chapl_aapl_',
               time_vec,
               '.png'),
        plot = y,
        dpi = 300,
        width = 25,
        height = 10,
        units = 'cm'
      )
    }
